### 2020-02-17 README.Rmd
Update README.Rmd

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/LiYingWang/kwl.pottery/master?urlpath=rstudio)

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/LiYingWang/kwl.pottery/master?urlpath=rstudio) [![run-docker](https://github.com/LiYingWang/kwl.pottery/workflows/.github/workflows/run-docker.yml/badge.svg)](https://github.com/LiYingWang/kwl.pottery/actions)
